---
title: "Temporal Charge Points Description"
output:
  html_document:
    theme: yeti
    smart: true
    highlight: textmate
    toc: true
    number_sections: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---


## Load packages


### Load basic package

```{r}
library(sp)
library(maptools)
library(tmap)
library(sf)
library(tmaptools)
library(tidyverse)
library(janitor)
library(spdep)
library(spatstat)
library(plyr)
library(stats)
library(corrr)
library(car)
library(tidymodels)
```

### load plot library

```{r}
library(ggplot2)
library(plotly)
library(RColorBrewer)
library(Rmisc)
```




## load data


### load obesity.csv file


```{r}
obesity_gender <- read_csv("datasets/obesity_gender_england.csv")
obesity_gender$year = c(2009:2019)
obesity <- read_csv("datasets/obesity_england.csv")
summary(obesity)
```

### load education investment.csv

```{r}
eduinves <- read_csv("datasets/education_investment.csv") %>% 
  select(., c(1, 7)) %>% 
  clean_names()
```


### load income.csv

```{r}
income_male <- read_csv("datasets/income_male.csv") %>% 
  select(., c(2, 6))
income_female <- read_csv("datasets/income_female.csv") %>% 
  select(., c(2, 6))
```



### load crime.csv


```{r}
# code translation
code <- read_csv("datasets/code.csv") %>% 
  select(., c(1, 3)) %>% 
  clean_names()
```

```{r}
crime <- read_csv("datasets/crime.csv") 
crime <- crime %>% 
  filter(.$`12 months ending`=="31/12/2018") %>% 
  select(., c(3, 6, 7)) %>% 
  clean_names() 

crime <- crime[!is.na(crime$ons_code),]
crime <- crime %>% 
  pivot_wider(id_cols = 1,
              names_from = offence,
              values_from = rolling_year_total_number_of_offences) 

```
```{r}
type <- crime %>% 
  summarise_all(class) %>% 
  pivot_longer(everything(),
               names_to="all_variables",
               values_to="variable_class")
type

```
```{r}
crime[is.na(crime)] <- 0
crime$sum = rowSums(crime[,2:22])
crime <- crime %>% 
  select(.,c(1, 23)) %>% 
  left_join(., code,
            by = c("ons_code" = "csp17cd"))
```


### load shapefile

```{r}
la <- st_read("datasets/gadm36_GBR_shp/gadm36_GBR_2.shp") %>% 
  st_transform(., 27700) %>% 
  clean_names()
```


##plot temporal change of obesity in male and female

```{r}
obesity_gender <- obesity_gender %>% 
  select(., c(4, 5, 6)) %>% 
  pivot_longer(.,cols = 1:2,
               names_to = "gender",
               values_to = "count") %>% 
  clean_names()
```

```{r}
ggplot(data = obesity_gender, mapping = aes(x = year, y = count, group = gender)) +
  geom_line(aes(color = gender))+
  geom_point(aes(color = gender))+
  xlab("Year")+
  ylab("Number of obesity (*1000)")+
  scale_x_continuous(breaks = seq(2009, 2019, by = 1))+
  scale_y_continuous(labels = function(y) y / 1000)+
  ggtitle("Trend of obesity prevalence in England by gender")+
  theme(axis.title = element_text(size=18),axis.text = element_text(size=16),
        strip.text = element_text(size=18))+
  theme_classic() 
```
```{r}
ggsave("pic/obesity trend by gender.jpg", width = 7, height = 4)
```


```{r}
unique(la$name_1)
```
```{r}
england_la <- la[la$name_1=="England",]%>% 
  select(., c(6, 7, 14)) 
```

## merge shapefile and .csv file of England

```{r}
england_obesity <- england_la %>% 
  left_join(., obesity,
            by=c("name_2"="X3")) %>% 
  select(., c(2, 3, 5, 6, 7, 9, 10, 11, 12)) %>% 
  clean_names()
```
```{r}
colnames(england_obesity)
```

```{r}
tm_shape(england_obesity) +
  tm_polygons("all_persons_per_100_000_of_population",
              palette=RColorBrewer::brewer.pal(8, "YlOrRd"),
              midpoint=NA)
```
```{r}
densityfun <- function(datasets, colname, number, mode){
  tmap_mode(mode)
  breaks = c(-Inf, 500, 1000, 1500, 2000, 2500, 3000, 3500, +Inf) 
  tm <- tm_shape(datasets) +
    tm_polygons(colname,
                breaks=breaks,
                palette=RColorBrewer::brewer.pal(8, "YlOrRd"),
                midpoint=NA) +
    tm_legend(show=FALSE)+
    tm_layout(frame=FALSE)+
    tm_credits(number, position=c(0,0.85), size=1)
  
  return(tm)
}

```
```{r}
legendfun <- function(datasets, colname){
  breaks = c(-Inf, 500, 1000, 1500, 2000, 2500, 3000, 3500, +Inf) 
  legend <- tm_shape(datasets) +
    tm_polygons(colname,
                breaks=breaks,
                palette=RColorBrewer::brewer.pal(8, "YlOrRd"), 
                title="Density of obese people in England \n(per 100,000 population)") +
    tm_scale_bar(position=c(0.4, 0.01), text.size=0.6)+
    tm_compass(north=0, position=c(0.95, 0.1))+
   
    tm_layout(title = "Obese Population Density Comparison", 
              legend.title.size=1,
              legend.text.size = 0.6,
              legend.only = TRUE, 
              legend.position=c(0.1,0.1),asp=0.1)
  
  return(legend)
}
```

### tmap - obese population density by LA in England

```{r}
tm1 <- densityfun(england_obesity, "male_per_100_000_of_population","a)", "plot")
tm2 <- densityfun(england_obesity, "female_per_100_000_of_population","b)", "plot")
```


```{r}
legend <- legendfun(england_obesity,"male_per_100_000_of_population")


t_density <- tmap_arrange(tm1, tm2, legend, ncol=3)
t_density
```
```{r}
tmap_save(t_density, 'pic/obese population density.png', width=7, height=3)
```


## merge datasets

```{r}
obesityfactor <- england_obesity %>% 
  left_join(., eduinves,
            by = c("region_and_la_of_residence" = "la_code")) %>% 
  left_join(., income_male,
            by = c ("region_and_la_of_residence" = "Code")) %>% 
  left_join(., income_female,
            by = c ("region_and_la_of_residence" = "Code")) %>% 
  left_join(., crime,
            by = c ("region_and_la_of_residence" = "lad17cd")) %>% 
  select(., c(2, 7, 8, 9, 10, 11, 13))

```

```{r}
colnames(obesityfactor) = c("code","male_obesity","female_obesity","education_invest",
                "male_income","female_income","crime", "geometry")
```
```{r}
obesityfactor <- obesityfactor[!is.na(obesityfactor$male_obesity)&
                                 !is.na(obesityfactor$female_obesity)&
                                 !is.na(obesityfactor$education_invest)&
                                 !is.na(obesityfactor$male_income)&
                                 !is.na(obesityfactor$female_income)&
                                 !is.na(obesityfactor$crime)&
                                 !is.na(obesityfactor$crime),]
```

## spatial autocorrelation

### Global Moran's I for obese male and female

```{r}
# check the current class
class(england_obesity)
# convert it to sp
england_obesity_sp <- as_Spatial(england_obesity, IDs=england_obesity$region_and_la_of_residence)
# check the class of the new object
class(england_obesity_sp)
```
```{r}
# make the nb
england_obesity_nb <- poly2nb(england_obesity_sp, row.names=england_obesity_sp$region_and_la_of_residence)
```
```{r}
# create the list weights object
nb_weights_list <- nb2listw(england_obesity_nb, style='B',
                            zero.policy = TRUE)
```

```{r}
moran(england_obesity$male_per_100_000_of_population, 
      nb_weights_list, 
      n=length(nb_weights_list$neighbours), 
      S0=Szero(nb_weights_list),
      zero.policy = TRUE)
```
```{r}
mc_model1 <- moran.mc(england_obesity_sp$male_per_100_000_of_population, nb_weights_list, nsim=999,zero.policy = TRUE)
mc_model1
```


```{r}
moran(england_obesity$female_per_100_000_of_population, 
      nb_weights_list, 
      n=length(nb_weights_list$neighbours), 
      S0=Szero(nb_weights_list),
      zero.policy = TRUE)
```
```{r}
mc_model2 <- moran.mc(england_obesity_sp$female_per_100_000_of_population, nb_weights_list, nsim=999,zero.policy = TRUE)
mc_model2
```
```{r}
# rescale that variable!
england_obesity_sp$scale_male_per_100_000_of_population <- scale(england_obesity_sp$male_per_100_000_of_population)
# create a spatial lag variable and save it to a new column
england_obesity_sp$lag_scale_male <- lag.listw(nb_weights_list, england_obesity_sp$scale_male_per_100_000_of_population)
england_obesity_moran_stats <- st_as_sf(england_obesity_sp)
local_moran <- localmoran(england_obesity_sp$male_per_100_000_of_population, nb_weights_list)
```

```{r}
sig_level <- 0.1

# version with significance value
england_obesity_moran_stats$obese_male_aggregation_spot <- ifelse(england_obesity_moran_stats$scale_male_per_100_000_of_population > 0 & 
                                            england_obesity_moran_stats$lag_scale_male > 0 & 
                                            local_moran[,5] <= sig_level, 
                                          "high-high", 
                                          ifelse(england_obesity_moran_stats$scale_male_per_100_000_of_population <= 0 & 
                                                   england_obesity_moran_stats$lag_scale_male <= 0 & 
                                                   local_moran[,5] <= sig_level, 
                                                 "low-low", 
                                                 ifelse(england_obesity_moran_stats$scale_male_per_100_000_of_population > 0 & 
                                                          england_obesity_moran_stats$lag_scale_male <= 0 & 
                                                          local_moran[,5] <= sig_level, 
                                                        "high-low", 
                                                        ifelse(england_obesity_moran_stats$scale_male_per_100_000_of_population <= 0 & 
                                                                 england_obesity_moran_stats$lag_scale_male > 0 & 
                                                                 local_moran[,5] <= sig_level, 
                                                               "low-high",
                                                               ifelse(local_moran[,5] > sig_level, 
                                                                      "not-significant", 
                                                                      "not-significant")))))

```
```{r}
# plot the results nnw with the satistical significance
ggplot(england_obesity_moran_stats, 
       aes(x = scale_male_per_100_000_of_population,
           y = lag_scale_male, 
           color = obese_male_aggregation_spot)) +
  geom_vline(xintercept = 0) + # plot vertical line
  geom_hline(yintercept = 0) + # plot horizontal line
  xlab("Scaled Male Obesity (n)") +
  ylab("Lagged Scaled Male Obesity (n)") +
  labs(colour="obese_male_aggregation_spot") +
  geom_point()
```
```{r}
tmap_mode("plot")
t1 <- tm_shape(england_obesity_moran_stats) +
  tm_polygons("obese_male_aggregation_spot",
              palette=c("red", "blue", "white", "grey"))+
  tm_legend(show=FALSE)+
  tm_layout(frame=FALSE)+
  tm_credits("a)", position=c(0,0.85), size=1)
```
```{r}
tmap_mode("view")
tm_shape(england_obesity_moran_stats) +
  tm_fill(col = "obese_male_aggregation_spot")
```

```{r}
# rescale that variable!
england_obesity_sp$scale_female_per_100_000_of_population <- scale(england_obesity_sp$female_per_100_000_of_population)
# create a spatial lag variable and save it to a new column
england_obesity_sp$lag_scale_female <- lag.listw(nb_weights_list, england_obesity_sp$scale_female_per_100_000_of_population)
england_obesity_moran_stats <- st_as_sf(england_obesity_sp)
local_moran <- localmoran(england_obesity_sp$female_per_100_000_of_population, nb_weights_list)
```

```{r}
sig_level <- 0.1

# version with significance value
england_obesity_moran_stats$obese_female_aggregation_spot <- ifelse(england_obesity_moran_stats$scale_female_per_100_000_of_population > 0 & 
                                            england_obesity_moran_stats$lag_scale_female > 0 & 
                                            local_moran[,5] <= sig_level, 
                                          "high-high", 
                                          ifelse(england_obesity_moran_stats$scale_female_per_100_000_of_population <= 0 & 
                                                   england_obesity_moran_stats$lag_scale_female <= 0 & 
                                                   local_moran[,5] <= sig_level, 
                                                 "low-low", 
                                                 ifelse(england_obesity_moran_stats$scale_female_per_100_000_of_population > 0 & 
                                                          england_obesity_moran_stats$lag_scale_female <= 0 & 
                                                          local_moran[,5] <= sig_level, 
                                                        "high-low", 
                                                        ifelse(england_obesity_moran_stats$scale_female_per_100_000_of_population <= 0 & 
                                                                 england_obesity_moran_stats$lag_scale_female > 0 & 
                                                                 local_moran[,5] <= sig_level, 
                                                               "low-high",
                                                               ifelse(local_moran[,5] > sig_level, 
                                                                      "not-significant", 
                                                                      "not-significant")))))

```
```{r}
# plot the results nnw with the satistical significance
ggplot(england_obesity_moran_stats, 
       aes(x = scale_female_per_100_000_of_population,
           y = lag_scale_female, 
           color = obese_female_aggregation_spot)) +
  geom_vline(xintercept = 0) + # plot vertical line
  geom_hline(yintercept = 0) + # plot horizontal line
  xlab("Scaled Female Obesity (n)") +
  ylab("Lagged Scaled Female Obesity (n)") +
  labs(colour="obese_female_aggregation_spot") +
  geom_point()
```
```{r}
tmap_mode("plot")
t2 <- tm_shape(england_obesity_moran_stats) +
  tm_polygons("obese_female_aggregation_spot",
              palette=c("red", "blue", "white", "grey"))+
  tm_legend(show=FALSE)+
  tm_layout(frame=FALSE)+
  tm_credits("b)", position=c(0,0.85), size=1)
```

```{r}
tmap_mode("view")
tm_shape(england_obesity_moran_stats) +
  tm_fill(col = "obese_female_aggregation_spot")
```

```{r}
legend <- tm_shape(england_obesity_moran_stats) +
  tm_polygons("obese_female_aggregation_spot",
              palette=c("red", "blue", "white", "grey"),
              title="Obese people aggregation spot in England") +
  tm_scale_bar(position=c(0.1,0.12), text.size=0.6)+
  tm_compass(north=0, position=c(0.65,0.2))+
  tm_layout(title = "Obesity spatial autocorrelation", 
            legend.title.size=1,
            legend.text.size = 0.6,
            legend.only = TRUE, 
            legend.position=c(0.1,0.25),asp=0.1)
```

```{r}
tmap_mode("plot")
local_moran <- tmap_arrange(t1, t2, legend, ncol=3)
local_moran
```
```{r}
tmap_save(local_moran, "pic/Local Moran's I, Obesity in England.png",width=7, height=4)
```


## correlation

```{r}
colnames(obesityfactor)
```

```{r}
q1 <- qplot(x = `education_invest`, 
           y = `male_obesity`, 
           data=obesityfactor,
           xlim = c(550, 1150))

#plot with a regression line
q1 + stat_smooth(method="lm", se=FALSE, size=1) 
qem <- q1 + stat_smooth(method="lm", se=FALSE, size=1) 
```
```{r}
q2 <- qplot(x = `education_invest`, 
           y = `female_obesity`, 
           data=obesityfactor,
           xlim = c(500, 1150))

#plot with a regression line
q2 + stat_smooth(method="lm", se=FALSE, size=1) 
qef <- q2 + stat_smooth(method="lm", se=FALSE, size=1) 
```
```{r}
q3 <- qplot(x = `male_income`, 
           y = `male_obesity`, 
           data=obesityfactor,
           xlim = c(550, 750))

#plot with a regression line
q3 + stat_smooth(method="lm", se=FALSE, size=1) 
qim <- q3 + stat_smooth(method="lm", se=FALSE, size=1) 
```

```{r}
q4 <- qplot(x = `female_income`, 
           y = `female_obesity`, 
           data=obesityfactor,
           xlim = c(350, 550))

#plot with a regression line
q4 + stat_smooth(method="lm", se=FALSE, size=1) 
qif <- q4 + stat_smooth(method="lm", se=FALSE, size=1) 
```

```{r}
q5 <- qplot(x = `crime`, 
           y = `male_obesity`, 
           data=obesityfactor,
           xlim = c(0, 50000))

#plot with a regression line
q5 + stat_smooth(method="lm", se=FALSE, size=1) 
qcm <- q5 + stat_smooth(method="lm", se=FALSE, size=1) 
```


```{r}
q6 <- qplot(x = `crime`, 
           y = `female_obesity`, 
           data=obesityfactor,
           xlim = c(0, 50000))

#plot with a regression line
q6 + stat_smooth(method="lm", se=FALSE, size=1) 
qcf <- q6 + stat_smooth(method="lm", se=FALSE, size=1) 
```

```{r}
multiplot(qem, qef, cols = 2)
```
```{r}
multiplot(qim, qif, cols = 2)
```
```{r}
multiplot(qcm, qcf, cols = 2)
```


## regression

```{r}
type <- obesityfactor %>% 
  st_drop_geometry() %>% 
  summarise_all(class) %>% 
  pivot_longer(everything(),
               names_to="all_variables",
               values_to="variable_class")
type

```
```{r}
obesityfactorfilter <- obesityfactor %>% 
  filter(education_invest>=500&
           education_invest<=1150&
           male_income>=550&
           male_income<=750&
           female_income>=350&
           female_income<=550&
           crime<=50000)
```
```{r}
type <- obesityfactorfilter %>% 
  st_drop_geometry() %>% 
  summarise_all(class) %>% 
  pivot_longer(everything(),
               names_to="all_variables",
               values_to="variable_class")
type

```
```{r}

Correlation_male<- obesityfactorfilter %>%
  st_drop_geometry() %>% 
  dplyr::select(c(2, 4, 5, 7))%>%
  correlate()
Correlation_male
```
```{r}

Correlation_female<- obesityfactorfilter %>%
  st_drop_geometry() %>% 
  dplyr::select(c(3, 4, 6, 7))%>%
  correlate()
Correlation_female
```


